Quality assurance of digital twins: An experience report in the automotive industry

### 2023-03-24 manuscripts/paper-1/main.tex
Redesigned the pictures to fit 15

    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Fidelity (a) and efficiency (b) levels have been demonstrated with simplified CAD drawings and 
        finite state machines.}~\label{fig:EfficiencyandFidelity}

@@

        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability has been demonstrated with simplified finite state machines. 
        Evolving the machines on the left side, needed effort 
        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}

>>>>

    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Fidelity and efficiency levels have been demonstrated with simplified CAD drawings.}~\label{fig:EfficiencyandFidelity}
    \end{figure}

@@

        \includegraphics[width = 0.9\textwidth]{Evolvability.png}
        \caption{Figure represents the demonstration of evolvability with the comparison between the first state machine(represented in black), and the evolved state machine(represented in green). The required effort
        to evolve from the black state machine to the green state machine could be evaluated as \textit{Evolvability}.}~\label{fig:Evolvability}
